Treefelling_test_for all trees

### 2021-07-26 R/Treefelling_test_for all trees.Rmd
Treefelling and corrections

```{r}
felling <- function (inventory, SelectedTrees) {

  # # Take selected trees
  # SelectedTrees <- inventory %>% 
  #   filter(Selected == "1") %>%
  #   dplyr::select(idTree,DBH,TrunkHeight,TreeHeight,CrownHeight,CrownDiameter,Selected, Xutm, Yutm)

@@

  ggplot() + # plot 2 polygones
    geom_sf(data = Trunk) +
    geom_sf(data = Crown)

  ggplot() +
    geom_sf(data = a) # plot the multypolygon

@@

  # Create a polygon ScndTrail
  pts = list(matrix(c(286520, 583134,
                      286520, 583240, 
                      286524, 583240, 
                      286524, 583134,
                      286520, 583134) # the return
                    ,ncol=2, byrow=TRUE)) # DBH en cm à passer en m

  (ScndTrail <- st_polygon(pts))

  ggplot() + 
    geom_sf(data = a) + # the tree
    geom_sf(data = ScndTrail) # the 2nd trail

@@

  ggplot() + # plot 2 polygones
    geom_sf(data = a) + # the tree (polygone)
    geom_sf(data = Foot) + # the foot of the tree (point)
    geom_sf(data = ScndTrail) + # the 2nd trail (polygone)
    geom_sf(data = NearestPoints) + # the shortest way from the foot to the trail (linestring)
    geom_sf(data = Trail) # the point on the ScndTrail closest to the location of the tree (Foot)

@@

  TurnedTrunkA <- RotatePolygon(Trunk, angle = 60 - theta, fixed = Foot) # turned trunk
  TurnedCrownA <- RotatePolygon(Crown, angle = 60 - theta, fixed = Foot) # turned crown
  TurnedTrunkB <- RotatePolygon(Trunk, angle = 300 - theta, fixed = Foot) # turned trunk (angle in the clockwise direction: 360-60-theta)
  TurnedCrownB <- RotatePolygon(Crown, angle = 300 - theta, fixed = Foot) # turned crown (angle in the clockwise direction)

  # For a random direction felling
  RandomAngle <- sample(c(0:180), size = 1)
  RandomTrunk <- RotatePolygon(Trunk, angle = RandomAngle, fixed = Foot) # turned trunk
  RandomCrown <- RotatePolygon(Crown, angle = RandomAngle, fixed = Foot) # turned crown

  FellingOuputs <- list(a = a,
                        Foot = Foot,
                        ScndTrail = ScndTrail,
                        NearestPoints = NearestPoints,
                        Trail = Trail,
                        TurnedTrunkA = TurnedTrunkA,
                        TurnedCrownA = TurnedCrownA,
                        TurnedTrunkB = TurnedTrunkB,
                        TurnedCrownB = TurnedCrownB,
                        RandomTrunk = RandomTrunk,
                        RandomCrown = RandomCrown)

@@

AllTheFellingTrees <- lapply(EachTree, function(element)
  felling(inventory, element))

# a <- st_union(st_union(AllTheFellingTrees[[1]]$a, AllTheFellingTrees[[2]]$a), AllTheFellingTrees[[3]]$a)

# Foot <- st_union(st_union(AllTheFellingTrees[[1]]$Foot, AllTheFellingTrees[[2]]$Foot), AllTheFellingTrees[[3]]$Foot)

@@

NearestPoints <-  st_union(st_union(AllTheFellingTrees[[1]]$NearestPoints, AllTheFellingTrees[[2]]$NearestPoints), AllTheFellingTrees[[3]]$NearestPoints)
# Trail <- Trail
TurnedTrunkA <- st_union(st_union(AllTheFellingTrees[[1]]$TurnedTrunkA, AllTheFellingTrees[[2]]$TurnedTrunkA), AllTheFellingTrees[[3]]$TurnedTrunkA)

TurnedCrownA <- st_union(st_union(AllTheFellingTrees[[1]]$TurnedCrownA, AllTheFellingTrees[[2]]$TurnedCrownA), AllTheFellingTrees[[3]]$TurnedCrownA)

TurnedTrunkB <- st_union(st_union(AllTheFellingTrees[[1]]$TurnedTrunkB, AllTheFellingTrees[[2]]$TurnedTrunkB), AllTheFellingTrees[[3]]$TurnedTrunkB)

TurnedCrownB <- st_union(st_union(AllTheFellingTrees[[1]]$TurnedCrownB, AllTheFellingTrees[[2]]$TurnedCrownB), AllTheFellingTrees[[3]]$TurnedCrownB)
# RandomTrunk <- RandomTrunk
# RandomCrown <- RandomCrown

ggplot() + # plot 2 polygones
  # geom_sf(data = a) + # the tree (polygone)
  # geom_sf(data = Foot) + # the foot of the tree (point)
  geom_sf(data = ScndTrail) + # the 2nd trail (polygone)
  geom_sf(data = NearestPoints) + # the shortest way from the foot to the trail
  # geom_sf(data = Trail) + # the point on the ScndTrail closest to the location of the tree (Foot)
  geom_sf(data = TurnedTrunkA) +
  geom_sf(data = TurnedCrownA) +
  geom_sf(data = TurnedTrunkB) +
  geom_sf(data = TurnedCrownB)
  # geom_sf(data = RandomTrunk) +
  # geom_sf(data = RandomCrown)

>>>>

```{r}
felling <- function (inventory, SelectedTrees, fuel, directionalfelling, advancedloggingparameters = loggingparameters()) {

  # Take selected trees
  # SelectedTrees <- inventory %>%
  #   filter(Selected == "1") %>%
  #   dplyr::select(idTree,DBH,TrunkHeight,TreeHeight,CrownHeight,CrownDiameter,Selected, Xutm, Yutm)

@@

@@

  # Create 2 polygons ScndTrail
  pol1 <- list(matrix(c(286503, 583134,
                        286503, 583240, 
                        286507, 583240, 
                        286507, 583134,
                        286503, 583134) # the return
                      ,ncol=2, byrow=TRUE)) 
  pol2 <- list(matrix(c(286650, 583134,
                        286650, 583240, 
                        286654, 583240, 
                        286654, 583134,
                        286650, 583134) # the return
                      ,ncol=2, byrow=TRUE))

  PolList = list(pol1,pol2) #list of lists of numeric matrices
  (ScndTrail = st_multipolygon(PolList))

@@

@@

  # For a random direction felling
  if(directionalfelling == "0" && (fuel !="1" |fuel !="2")){
    RandomAngle <- sample(c(0:180), size = 1)
    TrunkA <- RotatePolygon(Trunk, angle = RandomAngle, fixed = Foot) # turned trunk
    CrownA <- RotatePolygon(Crown, angle = RandomAngle, fixed = Foot) # turned crown
    TrunkB <- NULL
    CrownB <- NULL
  }

  # To direct only to avoid damage to future and reserve trees
  # if (directionalfelling == "1"&& (fuel !="1" |fuel !="2")) {
  #   
  #   
  # }

  # To direct to avoid damage to future and reserve trees + track orientation. Winching: Foot before.
  if(directionalfelling == "2"&& (fuel !="1" |fuel !="2")){
    TrunkA <- RotatePolygon(Trunk, angle = 240 + theta, fixed = Foot) # turned trunk
    CrownA <- RotatePolygon(Crown, angle = 240 + theta, fixed = Foot) # turned crown
    TrunkB <- RotatePolygon(Trunk, angle = 120 + theta, fixed = Foot) # turned trunk 
    CrownB <- RotatePolygon(Crown, angle = 120 + theta, fixed = Foot) # turned crown
  }

  # Fuelwood exploitation in the crowns
  if(fuel =="1" |fuel =="2"){

    TrailDist <- st_distance(Foot, Trail)

    # ADD SLOPE CRITERIA !!!

    if(TrailDist <= advancedloggingparameters$GrappleLength){ # <= 6m (= grapple length) -> winching by grapple
      TrunkA <- RotatePolygon(Trunk, angle = theta + 60 , fixed = Foot) # turned trunk
      CrownA <- RotatePolygon(Crown, angle = theta + 60 , fixed = Foot) # turned crown
      TrunkB <- RotatePolygon(Trunk, angle = 300 + theta, fixed = Foot) # turned trunk
      CrownB <- RotatePolygon(Crown, angle = 300 + theta, fixed = Foot) # turned crown
    } else { # > 6m -> winching by cable
      TrunkA <- RotatePolygon(Trunk, angle = 240 + theta, fixed = Foot) # turned trunk
      CrownA <- RotatePolygon(Crown, angle = 240 + theta, fixed = Foot) # turned crown
      TrunkB <- RotatePolygon(Trunk, angle = 120 + theta, fixed = Foot) # turned trunk 
      CrownB <- RotatePolygon(Crown, angle = 120 + theta, fixed = Foot) # turned crown
    }

  FellingOuputs <- list(a = a,
                        Foot = Foot,
                        ScndTrail = ScndTrail,
                        NearestPoints = NearestPoints,
                        Trail = Trail,
                        TrunkA = TrunkA,
                        CrownA = CrownA,
                        TrunkB = TrunkB,
                        CrownB = CrownB)

@@

AllTheFellingTrees <- lapply(EachTree, function(element)
  felling(inventory, element,  fuel = "2", directionalfelling = "2"))

a <- st_union(st_union(AllTheFellingTrees[[1]]$a, AllTheFellingTrees[[2]]$a), AllTheFellingTrees[[3]]$a)

Foot <- st_union(st_union(AllTheFellingTrees[[1]]$Foot, AllTheFellingTrees[[2]]$Foot), AllTheFellingTrees[[3]]$Foot)

@@

NearestPoints <-  st_union(st_union(AllTheFellingTrees[[1]]$NearestPoints, AllTheFellingTrees[[2]]$NearestPoints), AllTheFellingTrees[[3]]$NearestPoints)
# Trail <- Trail
TrunkA <- st_union(st_union(AllTheFellingTrees[[1]]$TrunkA, AllTheFellingTrees[[2]]$TrunkA), AllTheFellingTrees[[3]]$TrunkA)

CrownA <- st_union(st_union(AllTheFellingTrees[[1]]$CrownA, AllTheFellingTrees[[2]]$CrownA), AllTheFellingTrees[[3]]$CrownA)

TrunkB <- st_union(st_union(AllTheFellingTrees[[1]]$TrunkB, AllTheFellingTrees[[2]]$TrunkB), AllTheFellingTrees[[3]]$TrunkB)

CrownB <- st_union(st_union(AllTheFellingTrees[[1]]$CrownB, AllTheFellingTrees[[2]]$CrownB), AllTheFellingTrees[[3]]$CrownB)

ggplot() + # plot 2 polygones
  geom_sf(data = a, colour = "red") + # default tree position (polygone)
  geom_sf(data = Foot) + # the foot of the tree (point)
  geom_sf(data = ScndTrail) + # the 2nd trail (polygone)
  geom_sf(data = NearestPoints) + # the shortest way from the foot to the trail
  # geom_sf(data = Trail) + # the point on the ScndTrail closest to the location of the tree (Foot)
  geom_sf(data = TrunkA, colour = "green") + # Foot before
  geom_sf(data = CrownA, colour = "green") +
  geom_sf(data = TrunkB, colour = "green") +
  geom_sf(data = CrownB, colour = "green")
